Behavior Driven Development in Haskell

### 2012-05-29 paper.tex
Introduction (wip)

In BDD, all behavior should be documented, together with some
\emph{evidence} for that behavior.

@@

For code documentation, we make use of Hspec inspired by
RSpec~\cite{rspec} and we proposed some combinators to set
expectations about \emph{code example}\/s.

>>>>

In BDD, all behavior should be documented, together with some
\emph{evidence} for that behavior.  Hspec inspired by
RSpec~\cite{rspec} allows to document code with \emph{properties} and
\emph{code examples}, and create an informal specification document
from that.

We made two observations:
\begin{enumerate}
    \item
        Parts of a specification can be useful as user documentation.
    \item
        Doctest, a tool inspired by a Python module with the same
        name~\cite{doctest}, already allows to verify
        \emph{interactive examples} in Haddock comments.
\end{enumerate}

\noindent Doctest is not commonly described as a BDD tool, but we
think it fits the picture.
We show how to use Doctest and Hspec in combination to design,
document and test Haskell code.

@@

\begin{itemize}
    \item
        We proposed some combinators to set expectations about
        \emph{code examples}.
\end{itemize}
